An Experimental Evaluation of Hybrid Querying on Vectors

### 2025-11-04 VLDB2026/main.tex
ok

\begin{document}
	%\begin{sloppypar}
	\title{An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)}

@@

	\author{Yan Li}
	\affiliation{%
		\institution{Wuhan University of Technology}
	}

	\author{Bolong Zheng}
	\affiliation{%
		\institution{Huazhong University of Science and Technology}
	}
	%%
	%% The "author" command and its associated commands are used to define the authors and their affiliations.

@@

	\section{CONCLUSION}
	In this paper, we systematically evaluate various hybrid query methods, including multiple algorithms, vector databases, and libraries. We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm. Experiments show that existing algorithms still have significant shortcomings in scenarios such as large-scale data, complex queries, and resource constraints. There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms. Furthermore, the performance of range filtering algorithms remains limited under high-recall requirements and lacks support for multi-attribute queries. Notably, in some high-recall scenarios, some algorithms even perform worse than the baseline method (e.g., Faiss). In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction. \textcolor{black}{Additionally, exploring algorithms that support a combined and efficient use of attribute and range filtering is also an important research topic.}

>>>>

\begin{document}
	%\begin{sloppypar}
	\title{An Experimental Evaluation of Hybrid Querying on Vectors}

@@

	\author{Yan Li}
	\affiliation{%
		\institution{Wuhan University of Technology}
	}
	\authornote{Yan Li is the corresponding author}
	\author{Bolong Zheng}
	\affiliation{%
		\institution{Huazhong University of Science and Technology}
	}
	\authornote{Bolong Zheng is the corresponding author}
	%%
	%% The "author" command and its associated commands are used to define the authors and their affiliations.

@@

	\section{CONCLUSION}
%In this paper, we systematically evaluate various hybrid query methods, including multiple algorithms, vector databases, and libraries. We enrich the attribute information of the dataset and design a variety of experimental scenarios, and comprehensively analyze the performance of each algorithm. Experiments show that existing algorithms still have significant shortcomings in scenarios such as large-scale data, complex queries, and resource constraints. There are still significant deficiencies in the flexibility and Boolean logic support of attribute filtering algorithms. Furthermore, the performance of range filtering algorithms remains limited under high-recall requirements and lacks support for multi-attribute queries. Notably, in some high-recall scenarios, some algorithms even perform worse than the baseline method (e.g., Faiss). In the future, it is necessary to further explore the flexibility and robustness of attribute filtering algorithms, while improving the performance of range filtering algorithms is also an important direction. Additionally, exploring algorithms that support a combination of attribute and range filtering is also an important research topic.
In this paper, we systematically evaluate hybrid query methods across multiple algorithms, vector databases, and libraries. We enrich dataset attributes, design diverse scenarios, and analyze overall performance. Experiments show that existing algorithms still have significant shortcomings in scenarios such as large-scale data, complex queries, and resource constraints. Attribute filtering lacks flexibility and Boolean logic support, while range filtering remains weak under high-recall or multi-attribute conditions. Some even underperform the baseline (e.g., Faiss). Future work will focus on improving the flexibility and efficiency of filtering algorithms and exploring unified algorithms that integrate attribute and range filtering.

\begin{acks}
This work was supported in part by NSFC Grant No. 62372194 and by 2025 Open Research Program of the MIIT Key Laboratory for Software Integrated Application and Testing \& Verification.

\end{acks}
